---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rgrind <img src="man/figures/logo.svg" align="right" height="180" />

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://opensource.org/licenses/MIT)
<!-- badges: end -->

`rgrind` brings gamified, LeetCode-style algorithmic and data
wrangling challenges directly into your R console. Solve puzzles
against real test cases, get instant styled feedback with
explanations, and build a daily solving streak, all running locally,
with zero setup and zero cost.

## Why rgrind?

Popular coding practice platforms (LeetCode, HackerRank, Codewars)
barely support R. Existing R learning tools (like DataCamp) rely on
passive video courses in a browser. `rgrind` is different: it is
an active, in-console practice tool built specifically for R's own
idioms: vectorisation, the tidyverse, and statistical computing,
with nothing to install beyond the package itself.

## Installation

You can install the development version of rgrind from
[GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("DevWebWacky/rgrind")
```
```{r, include = FALSE}
options(rgrind.storage_dir = tempfile("readme_render_"))
dir.create(getOption("rgrind.storage_dir"))
```

## Quick example

```{r example}
library(rgrind)

my_solution <- function(x) sum(x[x %% 2 == 0], na.rm = TRUE)
run_challenge("sum_evens", my_solution)
```

## Browse available challenges

```{r grind}
list_challenges()
```

`rgrind` currently ships with 10 challenges across four
categories: Base R Optimisation, Tidyverse Wrangling, Vectorisation
Efficiency, and Statistical Algorithms, ranging from Easy warm-ups to
Medium/Hard puzzles.

## Track your progress

Every attempt is logged locally on your own machine, nothing is sent
anywhere. Check your stats and keep your streak alive:

```{r progress}
rg_stats()
rg_heatmap()
```

## License

MIT © Uwakmfon Paul
